### 2015-10-03 untitled.tex
edited untitled.tex

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen}  calculating the worst-case response time in the above case is already a very challenging problem. Nelissen et al. \cite{ecrts15nelissen} identify several misconceptions used in the literature for this problem. After excluding those misconceptions, deriving the worst-case response time of a computation segment in pseudo-polynomial time seems to be a very difficult problem. Due to \cite{ecrts15nelissen}, the only existing solution to derive the exact $W_k^{j}$ (and hence $R_k^j$) requires exponential time complexity. And, also recall the example in \ref{sec:unschedulable}. Even if the conversion is done precisely, the deferrable task system can be more pessimistic than the original self-suspending task system with respect to the schedulability.

>>>>

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen}  calculating the worst-case response time in the above case is already a very challenging problem. Nelissen et al. \cite{ecrts15nelissen} identify several misconceptions used in the literature for this problem. After excluding those misconceptions, deriving the worst-case response time of a computation segment in pseudo-polynomial time seems to be a very difficult problem. Due to \cite{ecrts15nelissen}, the only existing solution to derive the exact $W_k^{j}$ (and hence $R_k^j$) requires exponential time complexity. Furthermore, as demonstrated with the example in Section \ref{sec:unschedulable}, even if the conversion is done precisely, the transformed deferrable task set can be more pessimistic than the original self-suspending task set with respect to schedulability.
